---
title: "ADA Week 3 Homework"
author: "Nitin Verma"
date: "September 14, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Challenges for this week
This week's challenges were based on the usage of data classes such as matrices, and arrays. Here is my attempt at the challenges:

## Challenge 1:
- First, create a vector of 1 word character strings comprising the first line of the Gettysburg address: “Four score and seven years ago our fathers brought forth on this continent, a new nation, conceived in Liberty, and dedicated to the proposition that all men are created equal.”
- Then, extract every third element of this vector.
### Solution:
```{r}
library(stringr)
wordVector <- stringr::str_split("Four score and seven years ago our fathers brought forth on this continent, a new nation, conceived in Liberty, and dedicated to the proposition that all men are created equal.", " ")[[1]]
str(wordVector)
wordVector
wordVector[seq(from=1, to=length(wordVector), by=2)]
```

## Challenge 2 (solutions inline):
```{r}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
```
- Given the matrix, m, above, extract the 2nd, 3rd, and 6th columns and assign them to the variable x
```{r}
x <- m[,c(2,3,6)]
x
```
- Given the matrix, m, above, extract the 6th to 8th row and assign them to the variable x
```{r}
x <- m[6:8,]
x
```
- Given the matrix, m, above, extract the elements from row 2, column 2 to row 6, column 9 and assign them to the variable x
```{r}
x <- m[2:6, 2:9]
x
```

## Challenge 3:
- Construct a 4-dimensional, 400 element array (5 x 5 x 4 x 4) named a consisting of the numbers 400 to 1 (i.e., a descending series)
- Given this matrix, what would the following return?
  - a[1, 1, 1, 2]
  - a[2, 3, 2, ]
  - a[1:5, 1:5, 3, 3]
### Solution:
```{r}
a <- array(data=400:1, dim=c(5,5,4,4))
a
a[1, 1, 1, 2]
a[2, 3, 3, ]
a[1:5, 1:5, 3, 3]
```

##Challenge 4:
Create a list representing a simplified primate taxonomy.
### Solution:
```{r}
platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
anthropoidea <- list(platyrrhini=platyrrhini, catarrhini=catarrhini)

tarsiidae <- c("tarsiidae")
tarsioidea <- list(tarsiidae=tarsiidae)

haplorhini <- list(anthropoidea=anthropoidea, tarsioidea=tarsioidea)

lorisidae <- c("lorisidae")
galagidae <- c("galagidae")
lorisoidea <- list(lorisidae=lorisidae, galagidae=galagidae)

cheirogaleidae <- c("cheirogaleidae")
lepilemuridae <- c("lepilemuridae")
indriidae <- c("indriidae")
lemuridae <- c("lemuridae")
daubentoniidae <- c("daubentoniidae")
lemuroidea <- list(cheirogaleidae=cheirogaleidae, lepilemuridae=lepilemuridae, indriidae=indriidae, lemuridae=lemuridae, daubentoniidae=daubentoniidae)

strepsirhini <- list(lorisoidea=lorisoidea, lemuroidea=lemuroidea)

primates <- list(haplorhini=haplorhini, strepsirhini=strepsirhini)
primates
```

##Challenge 5:
- Store the following numbers as a 6 x 3 matrix: 3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2
- Then, do the following:
  - Coerce the matrix to a data frame.
  - As a data frame, coerce the second column to be logical-valued
  - As a data frame, coerce the third column to be factor-valued
### Solution:
```{r}
m <- matrix(data=c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow=6, ncol=3, byrow=TRUE)
m

df <- data.frame(m)
df

df[2] <- as.logical(df[[2]])
df

df[3] <- as.factor(df[[3]])
df
```
